\documentclass[11pt, line, margin]{res}

\usepackage{fontspec}
\usepackage{titlepages}


\name{Hannah Fouasnon }
\address{hannah@djz.com}
\address{503.964.2403}

\newcommand{\prettysection}[1]{\setromanfont{TitilliumTitle20}\section{#1}\setromanfont{TitilliumText22L}}

\begin{document}
\setromanfont{TitilliumTitle20}


\begin{resume}
\setromanfont{TitilliumText22L}
\prettysection{EDUCATION}
{\bf Reed College} -  Portland, OR; 2006-2010 \\ 
Bachelor of Arts in Mathematics. \\
Thesis: \textit{A Structural Analysis of Hartigan's Modal Method for
  Block Clustering}

{\bf Friedl\"{a}nder-Schule} - Berlin, Germany; 2005 \\
Completed course of study in German
language. 

{\bf Hartnackschule} - Berlin, Germany; 2005 \\ 
Completed course of study in German language. 

{\bf Mississippi School for Mathematics and Science} - Columbus, MS; 2003-2005 \\ 
Public, admissions-based, residential high school for juniors and seniors. 

\prettysection{EXPERIENCE}

{\bf Crossfader (formerly DJZ Inc), Cofounder & Developer} - San Francisco, CA; 2012-2014 \\
Crossfader is an djing app for your iPhone created by a small team of
developers. | Created bulk of all non-iOS systems, such as the backend
API and both websites, djz.com and crossfader.fm. | Core tools:
angular.js, Rails, AWS + heroku

{\bf Lucky Sort Inc., Cofounder & Developer} - Portland, OR; 2011-2012 \\
Lucky Sort was a big data, text analytics company acquired by
twitter in 2013. | Primary creator and maintainer of the data pipeline,
devops tools, data preprocessing using nlp tools.  Other roles
included nontechnical work, such as business relations and client
management. | Core tools: node.js, python, nltk, R, d3, aws, kafka, redis

{\bf Qmedtrix Inc., R\&D Engineer} - Portland, OR; July 2009-April 2011 \\
Qmedtrix Inc. is a 3rd-party medical billing adjudicator | Worked on a small team to develop a scalable platform for various
medical billing operations in the insurance industry, such as fraud detection, adjudication,
pricing, and automatic report generation.  | Core tools: Scala,
python, redis, rabbitmq, postgres, R (ggplot2), latex

{\bf Reed College, Teacher's Assistant} - Portland, OR;
Aug. 2008-Dec. 2008 \\
Assisted the Introduction to Computing class taught in the Fall 2008
semester. Helped run computing labs, graded homework, and kept office hours for


{\bf Texas A\&M University, MCTP Participant} - College Station,
  TX; Summer 2008 \\
Experienced gained in signal
and image analysis, using Fourier analysis, wavelets, and computer software such as
MatLab. 

{\bf Gulf Coast Research Lab, Summer Intern} - Ocean Springs, MS;
  Summers 2004-2006 \\
Studied a parasite that lives on the skin of stingrays; Gave a
lecture to the American Society of Parasitologists and the Mississippi Academy of
Sciences; Worked on NSF grant: Small Grants for Exploratory Research (NSF Award
No. 0608603). 

\prettysection{KEYWORDS}
{\bf Languages} Python, Scala, R, Javascript, Ruby \\
{\bf Frameworks, Databases, Tools} Rails, nginx, node.js,  angular.js,
backbone.js, redis, rabbitmq, kafka, kinesis, redshift, postgres,
mysql, aws, heroku, ggplot2, mongodb, web audio, latex, emacs, ubuntu \\
 
\end{resume}
\end{document}

